\textbf{ Joystream: A Protocol for User Governed Content Platforms }

### 2019-02-25 paper.tex
Fix grammar

\item
When the time limit for replication by all storage providers has been exceeded, the lead create distribution relationships for the record, based on local policy.

>>>>

\item
When the time limit for replication by all storage providers has been exceeded, the lead creates distribution relationships for the record, based on local policy.
